An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex
Adding surrogate to abstain example

The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\raf{cites}.
A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.

While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation, finocchiaro2018convex}\raft{others? already a bit much...}, these works are mostly concerned with point estimation problems.
Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.

@@

\subsection{Consistency of abstain surrogate and link construction}
\label{sec:abstain}
\raf{Jessie: could you add the definition of their surrogate and link?  Use eq:abstain-surrogate for the label}

\raf{Copied}
... given by Ramaswamy et al.~\cite{ramaswamy2018consistent}.
In their work, they provide a consistent, polyhedral surrogate for the abstain loss $\ell_{\abstain{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
\begin{align}\label{eq:abstain}
\ell_{\abstain{\alpha}}(r,y) := \begin{cases}
0 & r = y\\
\alpha & r = a\\
1 & otherwise
\end{cases}
\end{align}
Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.

The surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} for $\alpha = 1/2$ embeds the $n$ outcomes into the $n$ vertices of the $\ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
They go on to show consistency and provide a calibrated \jessiet{check that?} link function from their surrogate to $\ell_{\abstain{1/2}}$.

@@

The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
While of course several surrogates are known for this problem~\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}, they typically work in $n$ dimensions.
one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}

>>>>

The literature on convex surrogates focuses mainly on smooth surrogate losses~\raf{DKR;many more...}\jessiet{DKR, some of Bob's added.}\cite{crammer2001algorithmic,bartlett2006convexity,bartlett2008classification, duchi2018multiclass, williamson2016composite, reid2010composite}.
Nevertheless, nonsmooth losses, such as the polyhedral losses we consider, have been proposed and studied for a variety of classification-like problems\cite{ramaswamy2018consistent, boser1992training}\raf{cites} \jessiet{Do we want the SVM (Boser) cite?}.
A notable addition to this literature is~\citet{ramaswamy2018consistent}, who argue that nonsmooth losses may enable dimension reduction of the prediction space (range of the surrogate hypothesis) relative to smooth losses, illustrating this conjecture with a surrogate for \emph{abstain loss} needing only $\log n$ dimensions for $n$ labels, whereas the best known smooth loss needs $n-1$.
Their surrogate is a natural example of an embedding (cf.~Section~\ref{sec:abstain}), and serves as inspiration for our work.

While property elicitation has by now an extensive literature~\cite{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}\raft{others? already a bit much...}, these works are mostly concerned with point estimation problems.
Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}; note however that they consider single-valued properties, whereas properties elicited by general convex losses are necessarily set-valued.

@@

\subsection{Consistency of abstain surrogate and link construction}
\label{sec:abstain}
\raf{Jessie: could you add the definition of their surrogate and link?  Use eq:abstain-surrogate for the label}
Consider the $\abstain{1/2}$ property, where one wants to report the most likely outcome, conditioned on such a $p_y \geq 1/2$.
If there is no such $p_y$, then the $\abstain{1/2}$ property suggests we abstain from predicting any one outcome.

~\citet{ramaswamy2018consistent} provides a consistent, polyhedral surrogate for a particular case of the abstain loss $\ell_{\abstain{\alpha}}:[n] \cup \{a\} \to \reals$ defined:
\begin{align}\label{eq:abstain-discrete}
\ell_{\abstain{\alpha}}(r,y) := \begin{cases}
0 & r = y\\
\alpha & r = a\\
1 & \text{otherwise}
\end{cases}
\end{align}
Here, the report $a$ corresponds to ``abstaining'' from voting if the outcome of any outcome is not likely enough to occur.

The $\abstain{1/2}$ surrogate provided by Ramaswamy et al.~\cite{ramaswamy2018consistent} embeds the $n$ outcomes into the $n$ vertices of the $d := \ceil{\log_2(n)}$-dimensional hypercube (vertices in $\{\pm 1\}^n$), and embeds the abstain point at the origin.
They give the surrogate
\begin{equation}\label{eq:abstain-surrogate}
L_{\abstain{1/2}}(u, y) = \left(\max_{j \in [d]}\varphi(y)_j u_j + 1\right)_+
\end{equation}
Moreover, they go on to show consistency and provide a link function from their surrogate to $\ell_{\abstain{1/2}}$.
\begin{equation}\label{eq:abstain-link}
	\phi(u) = \begin{cases}
	a & \min_{i \in [d]} |u_i| \leq 1/2\\
	\varphi^{-1}(\sgn(-u)) &\text{otherwise}
	\end{cases}
\end{equation}
\jessiet{Note about how they have $\sgn(0) = 1$?}

@@

The construction given in Theorem~\ref{thm:discrete-loss-poly-embeddable}, together with the calibrated link construction in Section~\ref{sec:calibration}, can generate consistent convex surrogates for arbitrary discrete losses.
For example, consider cost-sensitive classification; given an arbitrary loss matrix $C \in \reals^{n\times n}_+$ describing the loss $\ell_j(i) = C_{ij}$ of predicting label $i$ when the true label is $j$, we construct a convex surrogate based on the convex conjugate of $-\risk{\ell}$.
While of course several surrogates are known for this problem~\cite{pires2013cost}\raf{Jessie, could you cite \url{http://proceedings.mlr.press/v28/avilapires13.pdf} here}, they typically work in $n$ dimensions.
one advantage of our embedding framework is the ability to construct lower-dimensional surrogates when costs have certain geometric interpretations.
For example, if $v_1,\ldots,v_n \in \reals^k$ are on the unit sphere and $C_{ij} = \inprod{v_i}{v_j}$, we can simply take $L_j(u) = $\raf{aaaand Noah woke up}
